Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
First version submitted
Still 16 hours to go, that is, until late tomorrow morning. I prefer to leave it this way, but if there's any major error, please let me know. Also check from the email you have received that it's done correctly.

thanks @fergunet @unintendedbear @mariosky @pacastillo for your help.

Using the browser as a computing resource in volunteer computing presents several advantages, 
but it remains a challenge to fully harness the browser's capabilities and
to model the user's behavior so that those capabilities can be
leveraged optimally. These are the objectives of this paper, where we present the results of several
evolutionary computation experiments with different implementations of
a volunteer computing framework called {\sf NodIO}, designed to be
easily deployable on freely available cloud resources. We use  
%Pablo: "deployable in using free cloud resources" is correct?
% why not? - JJ
% is easy deployable? yes! where? in free cloud resources! 
% is easy deployable? yes! when?  (when) using free cloud resources
% is one or the other, I like "on"   
% on it is. - JJ   
different implementations to find out which one is 
able to get the user to lend more computing cycles and test different
problems to check the influence it has on said performance, as
measured by the time needed to find a solution, but also by the number
of users that it is able to gather and keep. 
% Pablo: so the objective is "to determine which browser conf. is able
% to get more computing power from the users", it isn't? 
% (to keep this in mind the rest of the paper). What is a "browser configuration"?
% (explain it with a phrase in the abstract)
% No, we don't. Please read the paper!!!! - JJ
% FERGU: Sorry, JJ, but the objective is not clear to me yet here, 
% even if the implementation comparison I wrote is in the conclusions as the first 
% objective of the paper. Also, the metrics used should be mentioned in the abstract.
% For example: "The first objective of this paper is to compare different implementations 
% of NodIO (with and without Web Workers), measuring the time spent by the users. 
% The second objective is to model the user behavior by comparing whatever".
% Also, the two compared implementations (w and w/ Web Worker) should
% be mentioned.
% The objectives are in the first sentence. I have changed the second
% one to make it clearer - JJ
From these experiments we can already draw some conclusions, besides
the fact that volunteer computing can be a valuable computing
resource: the user has to be kept engaged in some way to be able to
use as many computing cycles as possible, the client has to be built
to use the computer capabilities fully, and, finally, the user
contributions follow a common statistical distribution. It is also
essential to be as open as possible with software and data.

>>>>

Using volunteer's browsers as a computing resource presents several
advantages, but it remains a challenge to fully harness the browser's
capabilities and to model the user's behavior so that those
capabilities can be leveraged optimally. These are the objectives of
this paper, where we present the results of several evolutionary
computation experiments with different implementations of a volunteer
computing framework called {\sf NodIO}, designed to be easily
deployable on freely available cloud resources. We use different
implementations to find out which one is able to get the user to lend
more computing cycles and test different problems to check the
influence it has on said performance, as measured by the time needed
to find a solution, but also by the number of users engaged.  From
these experiments we can already draw some conclusions, besides the
fact that volunteer computing can be a valuable computing resource and
that it is essential to be as open as possible with software and data:
the user has to be kept engaged to obtain as many computing cycles as
possible, the client has to be built to use the computer capabilities
fully, and, finally, that the user contributions follow a common
statistical distribution.
